Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-06 paper.qmd
Updated Figure 14

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 22

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc)

@@

## Compute hexbin parameters
num_bins_x_pbmc <- 13

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = tsne_pbmc, 
  num_x_bins = num_bins_x_pbmc)

@@

tr_from_to_df_pbmc <- tr_from_to_df_pbmc |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(19, 20, 23, 24, 29, 33, 48,
                     183, 181, 178, 176))) #19

tr_from_to_df_pbmc <- right_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc,
  by = c("from", "to")) |>
  select(-ID)

>>>>

<!--Fit the best model for author suggestion and compute error-->
```{r}
#| label: hexbin-pbmc
## Compute hexbin parameters
num_bins_x_pbmc <- 27

@@

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < 0.05)#benchmark_pbmc

@@

## Compute hexbin parameters
num_bins_x_tsne_pbmc <- 17

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = tsne_pbmc, 
  num_x_bins = num_bins_x_tsne_pbmc)

@@

# tr_from_to_df_pbmc <- tr_from_to_df_pbmc |>
#   mutate(ID = row_number()) |>
#   filter(!(ID %in% c(19, 20, 23, 24, 29, 33, 48,
#                      183, 181, 178, 176))) #19

tr_from_to_df_pbmc <- right_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc,
  by = c("from", "to")) #|>
  #select(-ID)
